Longitudinal analysis 

### 2020-04-12 docs/REVprod_analysis-long_invariance.rmd

```{r}
library(sjPlot)
library(dplyr)
library(lavaan)
library(stargazer)
library(corrplot)
library(psych)
library(knitr)
library(kableExtra)
```

```{r}
load(file = "input/data/proc/datawide_123.RData")
```

@@

```{r}
load(file = "input/data/proc/datalong.RData")     # Datos formato long
load(file = "input/data/proc/datawide_123.RData") # Datos formato wide 3 olas
load(file = "input/data/proc/dat04.RData")

>>>>

```{r}
library(sjPlot)
library(dplyr)
library(lavaan)
library(stargazer)
library(corrplot)
library(psych)
library(knitr)
library(kableExtra)
load(file = "input/data/proc/datawide_123.RData")
```

@@

```{r}
load(file = "input/data/proc/datalong.RData")     # Datos formato long
load(file = "input/data/proc/datawide_123.RData") # Datos formato wide 3 olas
